% !TEX root = hw1.tex

\section{Link Analysis [25 points]}

\subsection{Personalized PageRank I [12 points]}
Personalizing PageRank is a very important real-world problem: different users
find different pages relevant, so search engines can provide better results if
they tailor their page relevance estimates to the users they are serving. Recall
from class that PageRank can be specialized with clever modifications of the
teleport vector. In this question, we will explore how this can be applied to
personalize the PageRank algorithm.

Assume that people's interests are represented by a set of representative
pages. For example, if Zuzanna is interested in sports and food, then we could
represent her interests with the set of pages $\{$\texttt{www.espn.com},
\texttt{www.epicurious.com}$\}$. For notational convenience, we will use
integers as names for webpages.

Suppose you have already computed the personalized PageRank vectors for the following users:
\vspace{-0.25cm}
\begin{itemize}\setlength\itemsep{0pt}
\item Agatha, whose interests are represented by the teleport set $\{1,2,3\}$
\item Bertha, whose interests are represented by the teleport set $\{3,4,5\}$
\item Clementine, whose interests are represented by the teleport set $\{1,4,5\}$
\item Dolo, whose interests are represented by the teleport set $\{1\}$
\end{itemize}

Assume that the weights for each node in a teleport set are uniform.  Without
looking at the graph, can you compute the personalized PageRank vectors for the
following users? If so, how? If not, why not? Assume a fixed teleport parameter
$\beta$.

\vspace{-0.25cm}
\begin{enumerate}[i.]
\item \textbf{[4 points]} Eloise, whose interests are represented by the teleport set $\{2\}$.

\item \textbf{[4 points]} Felicity, whose interests are represented by the teleport set $\{5\}$.

\item \textbf{[4 points]} Glynnis, whose interests are represented by the teleport set $\{1,2,3,4,5\}$ with weights 0.1, 0.2, 0.3, 0.2, 0.2, respectively.
\end{enumerate}

\subsection{Personalized PageRank II [5 points]}

Suppose that you've already computed the personalized PageRank vectors of a set
of users (denote the computed vectors $V$). What is the set of all personalized
PageRank vectors that you can compute from $V$ without accessing the web graph?

\subsection{A different equation for PageRank [8 points]}
In class you that the PageRank equation can be written in different ways. You will prove this in this question.
Recall that the PageRank equation is:
\begin{align}
\label{equation:PageRank}
    \mathbf{r} = \mathbf{A} \mathbf{r},
\end{align}
where $\mathbf{r} \in \mathbb{R}^N$ is the PageRank vector, i.e. the vector of PageRank scores for each of the $N$ nodes, and (where $\mathbf{1}$ is the all-ones column vector of length $N$):
\begin{align}
    \mathbf{A} = \beta \mathbf{M} + \frac{1-\beta}{N}\mathbf{1}\mathbf{1}^\top.
\end{align}
Recall that here, $\mathbf{M}$ is the stochastic adjacency matrix, defined as
\begin{align}
    \mathbf{M}_{ij} = \left\{\begin{array}{lr}
        \frac{1}{d_j} , & \text{if (j,i) is an edge}\\
        0               & \text{otherwise}
        \end{array}\right\}
\end{align}
where $d_j$ is the degree of node $j$. Assume every node has degree at least 1.

Prove that (\ref{equation:PageRank}) is equivalent to
\begin{align}
    \mathbf{r} = \beta\mathbf{M} \mathbf{r}  + \frac{1-\beta}{N}\mathbf{1}.
\end{align}

Hint: Recall that $\mathbf{r}$ is normalized, i.e. $\sum_{i=1}^N \mathbf{r}_i = 1$.

\subsection*{What to submit}
\begin{enumerate}[2.1:]
\setcounter{enumi}{0}
\item
  \begin{itemize} \item  For each of $(i)$,$(ii)$, and $(iii)$, `yes' or `no' and a brief explanation of why or why not. \end{itemize}
  
\item
  \begin{itemize} \item A mathematical expression for the set in terms of $V$ and a brief explanation. \end{itemize}
  
\item
  \begin{itemize} 
  \item Proof that the two PageRank equations are equivalent.
  \end{itemize}

\end{enumerate}
